%=======================================================================
% abstract - 150 to 500 words
%=======================================================================
\singlespacing
\begin{abstract}
Cloud computing is a mature model of offering hardware and software components as services to clients, and constitutes a solid foundation for applications to be developed upon. Modern applications have performance, scalability and functionality demands that can largely benefit from the cloud ecosystem, where an application can be thought as a set of services and components working cooperatively to deliver a feature set. Those components can be very generic, like computing nodes, network infrastructure and databases, or more specific and feature-oriented.

Several cloud computing systems were built to ease the adoption and
usage of cloud computing by application developers. Tsuru is an open-source system for cloud computing, and offers the Platform-as-a-Service cloud service model. Tsuru provides a platform to run client applications, and a number of pluggable services that application developers can provision and integrate with the applications.

This work proposes an implementation of a cloud service for the Tsuru system to provide server push functionality. Server push is a programming model on client-server architectures where data is sent from the server to the client without an explicit request for that data. This functionality is usually found implemented at application level, coupling it with business and application logic, and bounding its scalability with the application. The model presented in this work decouples the server push functionality from the application, allowing independent management and scaling, as well as providing the functionality as a cloud service for the Tsuru platform, provisioning software and hardware components automatically for the application developer upon a call to the provisioner service.
\end{abstract}
\palavraschave{Cloud Service. Server Push. Cloud Computing. PaaS. Tsuru.}
